\begin{problem}
  {Q2(b)}
  Given a set of 4-tuples $(s_i, d_i, p_i, q_i)$, where each entry corresponds to source, destination, departure time, arrival time respectively, calculate
  the plan that arrives at $d_i$ as early as possible, while allowing for at least $1$ hour for each connecting flight. \\
  \begin{algorithmic}[1]
    \STATE Let $G(V,E)$ be an empty graph
    \FOR {$\forall (s_i, d_i, p_i, q_i)$}
    \STATE Create some vertex $v$ which corresponds to $s_i$
    \STATE Create some vertex $v'$ which corresponds to $d_i$
    \STATE Create a directed edge $e(v, v')$ with weight $q_i - p_i$
    \STATE Create a mapping $f: e \rightarrow (q_i + 1)$
    \STATE Create a mapping $g: e \rightarrow p_i$
    \ENDFOR
    \STATE Execute Dijkstra's algorithm starting at node $S$ and using $g(e)$ as the initial weight of any path starting with edge $e$
    \STATE Dovetail the following steps in between iterations of Dijkstra's algorithm.
    \FOR {$\forall e \in $current cutset}
    \IF {$f(e) > g(e)$}
    \STATE Remove $e$ from the graph
    \ENDIF
    \ENDFOR
  \end{algorithmic}
  \textbf{Runtime}\\
  The graph creation will explore every flight once, resulting in a complexity of $O(m)$. \\
  The additional steps in this algorithm will explore every node precisely once, so the complexity is $O(m)$. \\
  The runtime of this algorithm is $O(mlog(n))$ from Dijkstra's and $O(2m)$ from the additional steps. \\
  Therefore, the total runtime is $O(mlog(n))$ \\
  \textbf{Correctness}
  \begin{proof}
    An invalid edge is defined to be an edge where $q_i$ for an incoming flight and $p_i$ for an outgoing connection fulfill $p_i < q_i + 1$ \\
    By lines 6, 7, 12, the algorithm will delete such edges before they are explored by Dijkstra's algorithm. \\
    Each edge represents the total amount of time spent on the flight plus 1h overhead for connections. \\
    The initial weight (time) of any path is given to be the departure time of the edge explored. \\
    This means the lowest weight path will have the minimal time difference from $t=0$. \\
    Since there are no negative weight edges (time cannot be negative), Dijkstra's algorithm will successfully find the min weight path. \\
    This min weight path has the minimal time difference from $t=0$. \\
    This means the arrival time with respect to $t=0$ will be minimized. \\
  \end{proof}
\end{problem}
