\begin{problem}
    {Q2: 8.16}
    \textit{Intersection~Inference~Problem}: \\
    Given a finite set $U$ of size $n$ and collection $A_1, \dots, A_m$ of subsets of $U$, cardinalities $c_1, \dots, c_m$, does there exist
    a set $X \subset U$ such that $X \cap A_i = c_i$? \\
    Prove NP-Completeness
    \begin{algorithmic}[1]
    \STATE Let 3 disjoint sets $X, Y, Z$ of size $n$ and $T \subset X \times Y \times Z$ be an instance of 3D matching
    \STATE Let $m = |X \cup Y \cup Z|$
    \STATE Let $U$ be an initially empty set
    \STATE Let $A_1, \dots, A_m$ be initially empty sets
    \STATE Let $c_1, \dots, c_m = 1$
    \STATE $U := T$
    \FOR {$\forall v_i \in X \cup Y \cup Z$}
        \FOR {$\forall t_j = (x, y, z) \in T$}
            \IF {$v_i = x \lor v_i = y \lor v_i = z$}
                \STATE $A_i := A_i \cup t_j$
            \ENDIF
        \ENDFOR
    \ENDFOR
    \RETURN $Intersection-Inference(U, A_1, \dots, A_m, c_1, \dots, c_m)$
    \end{algorithmic}
    \noindent
    \textbf{Proof of correctness}:
    \begin{proof}
        Suppose there exists some $X$ which fulfills the Intersection Inference condition. \\
        By construction, $X \subset T$ \\
        Claim: $X$ contains at most one triple $(x,y,z)$ for each unique value of $x, y, z$ \\
        Suppose two triples in $X$ contain the same element. \\
        Without loss of generality, suppose this element is $x$ \\
        Find the set $A_i$ containing all triples that include $x$ \\
        Now, $|X \cap A_i| = 2$ because two triples contain $x$, both of which are in $A_i$ and both of which are in $X$ \\
        Contradiction. \\
        Claim: $X$ contains a triple containing each unique value at least once
        Suppose $X$ does not contain a triple that includes some unique value $v$. \\
        Find $A_i$ corresponding to $v$ \\
        $|X \cap A_i| = 0$ because $A_i$ contains only triples which include $v$ \\
        Contradiction
        Therefore, $X$ contains each element exactly once. \\\\
        Suppose there does not exist any $X$ which fulfills the Intersection Inference condition. \\
        Claim: There does not exist any 3D matching \\
        Suppose there existed a 3D matching. \\
        Take each triple $t_i$ in the 3D matching and let $X = \{t_i\}$ \\
        By the 3D matching problem statement, $X$ contains precisely 1 triple for every value $v \in X \cup Y \cup Z$ \\
        Take any arbitrary $A_i$ \\
        $|X \cap A_i| = 1$, because precisely one triple in $X_i$ contains the value associated with $A_i$ \\
        Contradiction. \\
    \end{proof}
    \noindent
    \textbf{Proof of runtime}:
    \begin{proof}
        Let $n$ be the cardinality $|X \cup Y \cup Z|$ \\
        Let $m$ be the cardinality $|T|$ \\
        For each element of $X \cup Y \cup Z$, the reduction checks each $t_i$ \\
        All other operations are constant time. \\
        Therefore, the reduction has runtime $\theta(mn)$ \\
        Let $N = max(|X|, |Y|, |Z|)$ \\
        We see $n = |X \cup Y \cup Z| \leq 3N$ \\
        Also, $m = |T| \leq N^3$ \\
        So the runtime as a function of the largest set is $\theta(N^4)$, which is polynomial.
    \end{proof}
\end{problem}
