\begin{problem}
  {Q1}
  Suppose you're consulting for a company that manufactures PC equipment and ships it to distributors all over the country.
  For each of the next $n$ weeks, they have a projected $supply s_i$ of equipment (measured in pounds), which has to be shipped
  by an air freight carrier.

  Each week's supply can be carried by one of two air freight companies, A or B.
  \begin{itemize}
    \item Company A charges a fixed rate $r$ per pound (so it costs $r \cdot s_i$ to ship a week's supply $s_i$)
    \item Company B makes contracts for a fixed amount $c$ per week, independent of the weight.
          However, contracts with company B must be made in blocks of four consecutive weeks at a time.
  \end{itemize}
  Give a polynomial-time algorithm that takes a sequence of supply values $s_1, s_2, \dots, s_n$ and returns a $schedule$ of minimum cost.
  $OPT(i)$
  \begin{algorithmic}[1]
      \IF {$i = 0$}
      \RETURN $0$
      \ENDIF
      \IF {$i < 0$}
      \RETURN $INVALID$
      \ENDIF
      \RETURN $min(rs_i + OPT(i-1), 4c + OPT(i-4))$
  \end{algorithmic}
  \noindent
  \textbf{Memoization}:
  Store an array of $[OPT(0), OPT(1), \dots, OPT(n)]$ \\
  Each element can be accessed in constant time by hashing based on $i$
  \noindent
  \textbf{Correctness}:
  \begin{proof}
    The schedule of using only Company A is explored by this algorithm. \\
    At every step of that schedule, the algorithm explores the possibility of using Company B. \\
    Therefore, the entire space of possible schedules is explored by the algorithm. \\
    By the last line of the algorithm, it will find the minimum cost schedule in the space of explored schedules. \\
  \end{proof}
  \noindent
  \textbf{Runtime}:
  \begin{proof}
      $OPT$ could possibly be computed for $n$ different values of $i$. \\
      Computing $OPT(i)$ will use two constant time lookups for $OPT(i-1)$ and $OPT(i-4)$ \\
      Therefore the worst case complexity is $O(n)$ \\
  \end{proof}
\end{problem}
