\begin{problem}
  {Q2(a)}
  Assume that you have to make change for $N$, and that you have an infinite supply of each $C = c_1, c_2, \dots, c_n$ valued coins where $1 \leq c_i \leq N-1$.
  Compute the minimum number of coins required to make the change. Provide an algorithm which solves the problem using dynamic programming, prove correctness and runtime.
  $OPT(C, N)$
  \begin{algorithmic}[1]
      \STATE $C = c_1, c_2, \dots, c_k$
      \IF {$C = \{\} \land N \neq 0 $}
      \RETURN $INVALID$
      \ENDIF
      \IF {$N = 0$}
      \RETURN $1$
      \ENDIF
      \IF {$N < 0$}
      \RETURN $INVALID$
      \ENDIF
      \RETURN $min(OPT(C - \{c_k\}, N), 1 + OPT(C, N-c_k))$
  \end{algorithmic}
  \noindent
  \textbf{Memoization}
  Store a collection of $k$ sparse arrays containing $OPT(C, N)$ \\
  Choose the array by keeping track of the number of elements in $C$, which can be done in amortized constant time. \\
  This is achieved by counting during the first iteration and keeping track of it through successive calls to $OPT$. \\
  Choose the index into the array using $N$, so the total lookup is amortized constant time. \\
  \noindent
  \textbf{Proof of correctness}
  \begin{proof}
      Suppose some particular combination of coins $C'$ is not explored. \\
      Let $C' = \{c_{1, 1}, \dots, c_{1, k_1}, \dots, c_{j, k_j}\}$ where the second subscript of each coin describes the individual instance of coin being used. \\
      Consider the following execution: \\
      First, $OPT$ line 11 uses case 2 $k_j$ times. \\
      Next, $OPT$ line 11 uses case 1. \\
      Next, $OPT$ line 11 uses case 2 $k_{j-1}$ times. \\
      Next, $OPT$ line 11 uses case 1. \\
      This repeats until all coins in $C'$ have been used. \\
      During this execution, the combination of coins $C'$ has been explored. \\
      This contradicts the original assumption.
  \end{proof}
  \noindent
  \textbf{Proof of runtime}
  \begin{proof}
      There are $n$ subsets of $C$ and $N$ values of $N$ which could be computed. \\
      We see that $OPT$ could be computed $N^2$ times in the worst case, since $1 \leq c_i \leq N-1$ \\
      Therefore the worst case runtime of this algorithm is $O(N^2)$, which is polynomial in $N$. \\
  \end{proof}
\end{problem}
